\documentclass{article}
\usepackage{listings}
\usepackage{xcolor}

\author{CASSIOUS KABWE}
\title{Statistical packages midterm}
\date{\today}

\begin{document}
\maketitle

\section{section 1:  Non-parametric Statistics (8.1, 8.2, 8.3)}
\begin{enumerate}
	\item Which of the following test is used to compare two independent samples when the dat is not normally distributed and the variances are not equal? \par 
    \textcolor{red}{\textit{Wilcoxon Rank-Sum Testt}}
        

    \item The Wilocoxon Rank-Sum Test is a non paramatic alternative to which paramatic tests? \par 
        \textcolor{red}{\textit{t-test}}
    
    \item In a Chi-square Test for Independence, what is the null hypothesis? \par 
        \textcolor{red}{\textit{The variables are independent}}

    \item You want to compare the median income of two different groups of people. Which non-paramatic test should you use? \par
        \textcolor{red}{\textit{Mann-Whitney U Test}}

    \section{Section 2: Advanced Data Analysis Techniques (Chapter 9)}

    \item In logistic regression, what type of variable is the dependent variable (the variable you are trying to predict)? \par
    \textcolor{red}{\textit{Categorical variable}}

    \item Which library is commonly used for time series analysis in Python? \par
    \textcolor{red}{\textit{Pandas}}
    

    \item In time series analysis, what is the moving average used for? \par
    \textcolor{red}{\textit{To smooth out noise and identify trends}}

    \item Which of the following is a supervised learning algorithm used for binary classification in scikit-learn? \par
    \textcolor{red}{\textit{K-Nearest Neighbors (KNN)}} 

    \item What is the purpose of training and testing datasets in machine learning? \par
    \textcolor{red}{\textit{To evaluate the model's perfomance and generalization}}

    \item Which of the following statements is true about overfitting in machine learning?
    \textcolor{red}{\textit{Overfitting ocurs when the models perfoms well on the training data but poorly on the testing data}}


    \item Write a Python code to perform the Kruskal-Walls Test on the following using Scipy library:
    \begin{verbatim}
        data-group1 = [23, 29, 32, 22, 28]
        data-group2 = [19, 18, 24, 25, 21]
        data-group3 = [16, 15, 14, 17, 20] 
    \end{verbatim}

    \begin{verbatim}
        from scipy.stats import kruskal

        data_group1 = [23, 29, 32, 22, 28]
        data_group2 = [19, 18, 24, 25, 21]
        data_group3 = [16, 15, 14, 17, 20]

        stat, p = kruskal(data_group1, data_group2, data_group3)

        print(p)
    \end{verbatim}

\end{enumerate}

\end{document}